%----------Chukwuemeka Mordi Resume----------
%%% If interested you can download code and run it


\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}





\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------


\begin{center}
    \textbf{\Huge \scshape Chukwuemeka E Mordi} \\ \vspace{1pt}
    \small 253-361-9028 $|$ \href{mailto:cmordi@uw.edu}{\underline{cmordi@uw.edu}} $|$ 
    \href{https://linkedin.com/in/chukwuemeka-mordi}{\underline{linkedin.com/in/chukwuemeka-mordi}} $|$
    \href{https://github.com/princezukoburner}{\underline{github.com/princezukoburner}}
\end{center}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University of Washington - Seattle}{Seattle, WA}
      {Bachelor of Science - Electrical and Computer Engineering}{Jun 2022 -- May 2024}
    \resumeSubheading
      {Green River College}{Auburn, WA}
      {Associate of Science - Computer Engineering}{Sep 2020 -- Jun 2022}
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

   \resumeSubheading
      {Data Analyst Intern}{Jul 2022 -- Sep 2022}
      {Expeditors}{Seattle, WA}
      \resumeItemListStart
        \resumeItem{Developed scripts and queries for data sets used to analyze ocean shipment times (\textbf{Python}, \textbf{SQL}). }
        \resumeItem{Performed data extraction from various databases using python drivers; transformed data using \textbf{pandas}; loaded data into \textbf{PostgreSql} database.}
        \resumeItem{Improved software integrity with data cleaning and validation of existing data sets to promote robust data management platform, resulting in data analysis and entry improvement by \textbf{12\%}.} 
      \resumeItemListEnd
      
% -----------Tips for Multiple Positions Heading-----------
%    \resumeSubSubheading
%     {Software Engineer I}{Oct 2014 - Sep 2016}
%     \resumeItemListStart
%        \resumeItem{Apache Beam}
%          {Apache Beam is a unified model for defining both batch and streaming data-parallel processing pipelines}
%     \resumeItemListEnd
%    \resumeSubHeadingListEnd
%-------------------------------------------

    \resumeSubheading
      {Product Management Intern}{Aug 2018 -- Sep 2018}
      {Google}{Johannesburg, South Africa}
      \resumeItemListStart
        \resumeItem{Achieved management recognition by designing and implementing projects aimed at retaining advertising clients.}
        \resumeItem{Produced high-quality documents, spreadsheets and presentations for internal and customer-facing
needs.}
        \resumeItem{Collaborated with company mentor to review best practices in software architecture.}
    \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
    
     \resumeProjectHeading
          {\textbf{Caesar Cipher} $|$ \emph{Python, Git}}{Dec 2022 -- Present}
          \resumeItemListStart
            \resumeItem{A python script to brute force Caesar Ciphers. Used as a tool in Capture The Flag competitions.}
             \resumeItemListEnd
    
      \resumeProjectHeading
          {\textbf{Monkeypox Predictive Analysis} $|$ \emph{Python, pandas, Matplotlib, NumPy, Git}}{Aug 2022 -- Present}
          \resumeItemListStart
            \resumeItem{Conducted Exploratory Data Analysis of the Monkeypox outbreak.}
            \resumeItem{Developed engineering features such as heat maps, outlier detection and distribution curves.}
             \resumeItemListEnd
             
      \resumeProjectHeading
          {\textbf{Redfin End to End Pipeline} $|$ \emph{Python, PostgreSQL, AWS, SQL, Spark, Git}}{Jul 2022 -- Present}
          \resumeItemListStart
            \resumeItem{Scraped all housing data on the market in addition to recently sold homes.}
            \resumeItem{Generated a Postgres DB to store both parsed and historical data.}
     \resumeItemListEnd
     
    \resumeSubHeadingListEnd

%-----------Notable Achievements-----------
\section{Notable Achievements}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{South African Mathematics Olympiad} $|$ \emph{Top 100 out of 86000+ (Final Round)}}{Jul 2019}
        
      \resumeProjectHeading
          {\textbf{South African Mathematics Olympiad} $|$ \emph{Top 15\% (Second Round) }}{Apr 2018}
\resumeSubHeadingListEnd
%
%-----------PROGRAMMING SKILLS-----------
\section{Additional}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     {\textbf{Relevant Coursework}}{: Data Structures and Algorithms, Linear Algebra, Discrete Math, Differential Equations, Database Systems, (Calculus I, II, III, IV)}\\
     \textbf{Programming Languages}{: Python, Java, SQL} \\
     \textbf{Other}{: Git, Apache Spark, MySQL, PostgreSQL, pandas, Matplotlib, NumPy, Google Cloud Platform, AWS, Tableau, BigQuery} \\
    }}
 \end{itemize}


%-------------------------------------------
\end{document}
